Bayesian Insights into Aerial Bombing Strategies: An Ordered Logistic Regression Analysis of WWII Target Prioritization Against Germany

### 2024-04-18 paper/paper.qmd
add model justification to result

The analysis revealed distinct patterns in target prioritization, highlighting the role of industry type and the mission’s originating country in determining target selection, while the impact of tonnage and aircraft numbers was relatively subdued. @tbl-model_summary.

>>>>

## Model Justification
The analysis revealed distinct patterns in target prioritization, highlighting the role of industry type and the mission’s originating country in determining target selection, while the impact of tonnage and aircraft numbers was relatively subdued. @tbl-model_summary.
